parental migration and adolescents educational performance

### 2022-06-25 data/Gu-thesis-script.Rmd
write up main text, put more visuals in appendix

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
library(cobalt) 
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

@@

```{}
set.seed(1)
d %>% select(
  w1chn_100:w2eng_100) %>%
ggplot(aes(x=w1chn_100:w2eng_100)) + 
  geom_boxplot(alpha=0.2)
```

@@

## Descriptive statistics
```{r}
d_migr <- d_cl %>%
  select(
  migr, migr_mo_only, migr_fa_only, migr_both,
  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) %>%
  remove_labels()
```

@@

```{r}

@@

```{r}
#table_control_variable <- 
table_balance <- st(
  d_ctvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return")
#table_control_variable 
```

```{r}
table_control_variable <- datasummary_skim(
  data = d_ctvar,
  type = 'categorical',
  output = 'markdown'
)
```

@@

Whole sample summary
```{r}
table_sum <- st(
  d_migr,
  digits = 2, 
  out = 'kable')
table_sum
```

```{r}
table_sum_migr <- st(
  d_migr,
  group = 'Parental Migration', 
  digits = 2, 
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
table_sum_migr
```

@@

```{r}
sum_m.out_fa_only <- summary(m.out_fa_only)
fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
```

@@

```{r}
d_fa_only <- d_cl %>% drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_fa_only ~ ctyids
  )
sum_m.out_fa_only <- summary(m.out_fa_only)
fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
```
```{r}
love.plot(
  m.out_fa_only,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  )
```

@@

>>>>

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
library(labelled)
library(cobalt) 
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) %>% remove_labels()
```

@@

@@

## Descriptive statistics
```{r}
d_migr <- d_cl %>%
  select(
  migr, migr_mo_only, migr_fa_only, migr_both,
  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) 
```

@@

@@

```{}
#table_control_variable <- 
table_balance <- st(
  d_ctvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return")
#table_control_variable 
```

```{r}
table_control_variable <- datasummary_skim(
  data = d_ctvar,
  type = 'categorical',
  output = 'markdown'
)
table_control_variable
```

@@

Whole sample summary
```{}
table_sum <- st(
  d_migr,
  digits = 2, 
  out = 'kable')
table_sum
```

```{}
table_sum_migr <- st(
  d_migr,
  group = 'Parental Migration', 
  digits = 2, 
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
table_sum_migr
```

@@

```{r}
sum_m.out_mo_only <- summary(m.out_mo_only)
fig_msmd_mo_only <- plot(sum_m.out_mo_only, xlim = c(0, 0.55), position = 'right')
```

@@

```{r}
d_fa_only <- d_cl %>% drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_fa_only ~ ctyids
  )
sum_m.out_fa_only <- summary(m.out_fa_only)
fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
```

```{r}
love.plot(
  m.out_mo_only,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  )
```

```{r}
love.plot(
  m.out_fa_only,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  )
```

@@

```{r}
bal.tab(m.out)
```
